\begin{abstract}
Programmers frequently turn to the web to solve problems and find example code.
Online instructions gloss over the syntax and purpose of snippets in supplemental languages like CSS selectors and terminal commands for the sake of brevity. \marti{Alternative: For the save of brevity, the snippets in online instructions often gloss over the syntax of languages like CSS selectors and unix commands.}
This leaves programmers on their own to resolve errors and modify code by using external documentation. \marti{Alternative: Programmers must compensate by consulting external documentation.}
In this paper, we propose language-specific routines called \Glspl{name} that automatically generate \emph{context-relevant, on-demand} \glspl{exp} of code.
A \Gls{name} detects explainable code in webpages, parses it, and generates in-situ natural language explanations and demonstrations of code. \marti{Alternative: "a web page" rather than "webpages" since the rest of the items in this sentence are singular.}
By building \glspl{name} for CSS selectors, regular expressions and  wget \marti{Should this be "the unix command "wget"?}, we demonstrate techniques for generating natural language explanations through template instantiation, synthesizing code demonstrations by parse tree traversal, and building compound explanations of co-occurring options. \marti{This sentence is too complex and would be better broken into two I think.}
Through a qualitative study, we show that \gls{name}-generated explanations can reduce the need for reference documentation in code modification tasks for CSS selectors and wget commands. \marti{Why is the second Tutoron capitalized, but the rest lower cased?}
\end{abstract}
