\section{Related Work}

\andrew{What about commercial systems?}

Our work draws upon ideas from 3 lines of inquiry:
helping programmers use the web to solve problems,
writing good technical documentation,
and generating and augmenting tutorials.

\subsection{Helping Programmers Use the Web to Solve Problems}

Recent studies have explored programmers' practice of opportunistic programming~\cite{brandt_two_2009}\cite{brandt_example-centric_2010}\cite{hartmann_hacking_2008}.

Still, both experienced programmers~\cite{duala-ekoko_asking_2012} and end-user programmers~\cite{dorn_lost_2013}\cite{dorn_learning_2010}\cite{rosson_everyday_2004} struggle to leverage web documentation to solve programming problems.
\andrew{TODO: read~\cite{dorn_learning_2010}\cite{rosson_everyday_2004}.}

Formally, we can look at these programming challenges as Ko et al.'s end-user programming learning barriers~\cite{ko_six_2004}.
For example, users may encounter the $selection$ barriers when trying to find APIs that will help them perform new tasks.
When troubleshooting the program, they may face the $understanding$ barrier to debug system output, or the $information$ barrier to try to learn more about silent failures.
Furthermore, programmers who develop a poor mental model of programming techniques~\cite{winslow_programming_1996} that they find online may find this to be an impediment during later learning.
\andrew{Make sure we're not misquoting the Winslow reference.}

Over the last couple of decades, a variety of systems and tools have been developed to support programmer learning in the wild
(i.e. outside the on-campus or online classroom).
Some of these are general purpose tools to promote problem solving and self-led informal learning.
The Idea Garden~\cite{cao_barriers_2012}\cite{cao_end-user_2013} provokes users to answer solve their own problems by asking 3 types of questions designed to help them think and seek new information productively.
\andrew{be specific.}
ScriptABLE~\cite{dorn_scriptable_2011} wraps online tutorials as `informal learning cases' to improve users' abilities to take lessons away from them. 
\andrew{be specific.}
\andrew{Is this actually for programming tasks or just general tasks?}

Additionally, researchers have recommended strategies for improving supporting debugging and development tasks.
Gross \& Kelleher~\cite{gross_non-programmers_2010} recommend strategies for non-programmers to understand unfamiliar code in the Storytelling Alice programming environment.
\andrew{double check}.
In the same line of inquiry, Gross et al. present Dinah~\cite{gross_dinah_2011} to help non-programmers select code for reuse based on its graphical output instead of the source alone.
Grigoreanu~\cite{grigoreanu_end-user_2012} recommend two strategies for sensemaking during end-user debugging.
Webcrystal~\cite{chang_webcrystal_2012} generates explanations of user-selected elements of HTML pages to help webpage authors better understand how to construct similar pages.
The Whyline~\cite{ko_designing_2004} answers programmers `why did' questions about program behavior in terms of runtime events in the Alice programming environment.

\subsection{Writing Good Instructions}

Minimal instruction theory provides guidelines for developing usable technical documentation~\cite{carroll_nurnberg_1990}.
There are three main insights of the minimalist approach:
learners are allowed to start immediatedly on meaningfully realistic tasks,
the amount of reading and other passive activity in training is reduced,
and errors and error recovery are presented in a way to make them less traumatic and more pedagogically productive.
Interstingly, today we find ourselves at a where that much of the typical programming documentation is no longer developed by professionals.
Programmers increasingly use \emph{crowd documentation}~\cite{parnin_measuring_2011} found on the web that may be written by hobbyists without formal training writing usable documentation and who do not have QA resources to cross-check documents' quality.
\andrew{Is this the right reference for the term crowd documentation?}

When it is not possible to produce minimal instruction that has been iteratively tested and tailored to its audience, Farkas recommends \emph{layered documentation}~\cite{farkas_layering_1998}.
Layered documentation allows users to access more \emph{backup information} for tasks like error recognition and correction, and enables the same documentation to be used by readers from different backgrounds.
We position our work with the core belief that minimal instruction is a worthwhile but likely unattainable standard for online programming tutorials.
Given the diverse audiences of programming tutorials and the lack of documentation expertise of their authors, minimal instruction seems impossible to achieve.
We therefore adapt Farkas's advice with a technique for adding interactive layering to existing tutorial documentation on the web.
Through this, we approach the aims of minimal instruction: improved transfer of tutorial skills to personal tasks, less web search for discovering background knowledge, and faster error recovery.

Eiriksdottir \& Catrambone~\cite{eiriksdottir_procedural_2011} detail three types of instructions --- procedures, principles, and examples --- and their pedagogical aims.
Detailed procedures and relevant examples are likely to ease users' initial task performance.
More abstract procedures promote good learning and transfer.
We believe that \glspl{name} can improve relevance of more general procedures by providing just-in-time description of configurable parameters of APIs.
Furthermore, they can be used to describe relevant principles and interactive examples to aid transfer beyond the current task.

\andrew{Also possibly relevant:~\cite{ames_just_2001}, for when and how to intervene with instructions.}

\subsection{Generating and Augmenting Tutorials}

Given users' growing dependence on tutorials for learning how to perform workflows in creative tools, programming, and beyond, there has been recent interest in understanding, generating and automatically augmenting tutorials.

\subsubsection{Measuring tutorial quality}

Lafreniere et al.~\cite{lafreniere_understanding_2013} determined the type of activites that users engage in through comment-based discussion following the body of tutorials.
\andrew{What were the activities, how do people learn from tutorials, what are their weaknesses?}
In the programming domain, Parnin \& Treude~\cite{parnin_measuring_2011} find that 87.4\% of the methods of the jQuery API are described by a blog post in the first 10 web search results.
Of these blog posts, about half were tutorials.

In a survey of 154 Photoshop tutorials, Lount \& Bunt~\cite{lount_characterizing_2014} harvested tutorials from an application-centered community, tutorial aggregator, tutorial factory, and popular tutorials via the CUTS tecnique~\cite{fourney_characterizing_2011}.
Among other findings, Lount \& Bunt describe strengths and weaknesses of the corpus as a whole.
Almost all tutorials included source files (90.3\%), the initial image (91.6\%), final image (96.7\%), at least one image per step (84.4\%), and references to past steps when repeated steps were used (89.6\%).
However, 40.7\% of tutorials contained no attempts to address potential errors, 83.1\% omitted any version information, and only 1 of every 20 steps had any explanation.
Mechanisms to improve such tutorials' coverage of potential efforts and explanation of tools used could improve the quality of the average online tutorial.

\subsubsection{Understanding tutorial content}

As the number of tutorials accessible to learners grows, it is increasingly important to understand the structure and semantics of tutorial content to enable users to compare workflows and so that tutorials can be more easily augmented with interactivity.
Lau et al.~\cite{lau_interpreting_2009} produce keyword, grammar, and machine learning-based methods for determining segments of how-to instruction text that describe web application interactions.
Fourney et al.~\cite{fourney_then_2012} develop a method for detecting references to UI elements within tutorial text.
With a corpus of 35 documents from GIMP documentation, they achieve an F1-score of 0.81 for classifying words as labels for widgets.
\andrew{Does citation go at end of sentence or by the author name?}
Delta~\cite{kong_delta_2012} and Sifter~\cite{pavel_browsing_2013} extract commands from tutorials for creative tools.
User interfaces for these systems enable users to compare multiple workflows that have the same goal.
\andrew{Does Delta actually extract features, or rely upon manual labels?}
\andrew{I'm positive there's work here that I've missed.}

\subsubsection{Authoring, generating, and improving tutorials}

As authoring helpful tutorials is a non-trivial task requiring time and effort, recent work has sought to produce guidelines and techniques for automatically generating rich, useful tutorials.
Ginosar et al.~\cite{ginosar_authoring_2013} built a framework for easing the creation and editing of multi-stage programming tutorials.
Harms et al.~\cite{harms_automatically_2013} enable middle school programming learners to generate tutorials from code snippets.
Tools have been created for the creation of step-by-step mixed media tutorials~\cite{chi_mixt_2012}, instructional videos for physical demonstrations~\cite{chi_democut_2013}, and graphic design workflows~\cite{grossman_chronicle_2010}.
\andrew{I'm positive there's work here that I've missed.}

There has been interest in leveraging the online community to improve existing online tutorials.
Two methods proposed for this include labeling subgoals in how-to videos~\cite{kim_learnersourcing_2013} and linking a tutorial to alternate demonstrations~\cite{lafreniere_community_2013}.
\andrew{TODO read~\cite{kim_learnersourcing_2013}\cite{lafreniere_community_2013}.}
Similar to this past line of research, we seek methods for augmenting existing tutorials.
To our knowledge, we are the first to ask how automic community tutorial maintenance efforts can be applied beyond the current tutorial to the a body of related online tutorials.

Similar to our system, the commercial browser extension Diigo\footnote{\url{www.diigo.com}} lets users mark up HTML web pages with persistent comments and socially share these comments.
